---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# namsor

<!-- badges: start -->
<!-- badges: end -->

The goal of `namsor` is to provide some functionality to use some endpoints
for namsor's name checking API service. One can use this to for retrieve 
best estimations for a name's gender and/or ethnicity.


## Installation

You can install the development version of `namsor` like so:

``` r
require(remotes)
remotes::install_github('SinanPolatoglu/namsor')
```

## Usage

Obtain an API key via namsor.com

```{r lib}
library(namsor)

## SET API KEY
# Sys.setenv(NAMSOR_API_KEY='your api key')
```

Supported endpoints currently are

- `namsor_gender`
- `namsor_origin`
- `namsor_country`
- `namsor_diaspora`

Result in case of a succesful call will be as list with the retrieved output.
For example:
```{r examples}
str(namsor_origin('Sinan', 'Polatoglu'))
```
